### 2019-05-31 Documents/literature_review/pages/review_content.tex
Changes; - Added TODOs
Changes; - Quantified accuracy with a table - Added results for speed of comparison - Small wording changes

\textbf{TODO: } - Create written introduction setting the scene.
\textbf{TODO: } - Summarise research questions after lit' review. Back them up using my discussion.
% \textbf{TODO: } - Check evaluation with each paper in regards to:
% \begin{itemize}
%     \item Participant size [P]
%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
%     \item Target entropy [E]
%     \item Attacker strength [A]
% \end{itemize}
% [P, S, E, A]

@@

The paper touches upon issues with decentralised methods of identification such a PGP's Web of Trust and the problems these solutions have with user adoption. These points are made in an attempt to validate the requirement for manual comparison of key based fingerprints. This is a common theme that appears in the majority of the reviewed papers. Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems. Examples of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios. These are, however, acknowledged as limitations in the later stages of the paper. The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint. This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker. Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered another limitation.

@@

@@

>>>>

\textbf{TODO: } - Create written introduction setting the scene. \\
\textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
\textbf{TODO: } - Create a background section for Compare-and-X

% \textbf{TODO: } - Check evaluation with each paper in regards to:
% \begin{itemize}
%     \item Participant size [P]
%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
%     \item Target entropy [E]
%     \item Attacker strength [A]
% \end{itemize}
% [P, S, E, A]

@@

The paper touches upon issues with decentralised methods of identification such a PGP's Web of Trust and the problems these solutions have with user adoption. These points are made in an attempt to validate the requirement for manual comparison of key based fingerprints. This is a common theme that appears in the majority of the reviewed papers. The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint. This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker. Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered a limitation.

@@

To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results}. Each paper used a unique, and, therefore, have been translated into overall accuracy. Due to some of the differing characteristics of the papers ultimatly affecting results, Table \ref{tab:attacker} has also be provided. This table is useful to compare the health of the study and chosen sizes that may affect the accuracy and reliability of the results.

\textbf{TODO:} Usability table

\begin{table}
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_comparison.tex}
    }%
    \caption{Accuracy comparison of textual and graphical encoding schemes}
    \label{tab:results}
\end{table}

\begin{table}
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_attacker_stren.tex}
    }%
    \caption{Paper attribute comparison}
    \label{tab:attacker}
\end{table}

@@

\section{Research Questions}
\textbf{TODO: } - Backup choice of questions up using my previous discussion.
